Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-21 Paper/ms.tex
Marginal likelihoods, words on Gliese 581

\section{Inference}
Bayesian inference is the use of probability theory to describe uncertainty
\citep{}. In this framework, we approach data analysis problems by first
constructing a {\it hypothesis space}, which is the set of possible answers
to the problem we are considering. Normally, this is the set of possible
values of a vector of parameters $\btheta$ whose values we want
to know. We then assign probability distributions
called the {\it prior} and the {\it sampling distribution}. The prior
distribution $p(\btheta)$ describes
our initial uncertainty about which values of the parameters
$\btheta$ are plausible, and the
sampling distribution $p(\bdata | \btheta)$ describes
our initial uncertainty about the data set we're going to observe, as a
function of the unknown parameters $\btheta$.
When the data is known, our state of knowledge about the parameter is
updated from the prior $p(\theta)$ to the posterior distribution given by
Bayes' rule:
\begin{eqnarray}
p(\btheta | \bdata) &=&
\frac{p(\btheta)p(\bdata | \btheta)}
{p(\bdata)}
\end{eqnarray}
where the denominator, often called the {\it evidence} or
{\it marginal likelihood}, is given by:
\begin{eqnarray}
p(\bdata) = \int p(\btheta) p(\bdata | \btheta) d^N \btheta
\end{eqnarray}

@@

@@

@@

>>>>

\section{Inference}
Bayesian inference is the use of probability theory to describe uncertainty
\citep{}. In this framework, we approach data analysis problems by first
constructing a {\it hypothesis space}, which is the set of possible answers
to the problem we are considering. Normally, this is the set of possible
values of a vector of parameters $\btheta$ whose values we want
to know. We then assign probability distributions
called the {\it prior} and the {\it sampling distribution}. The prior
distribution $p(\btheta)$ describes
our initial uncertainty about which values of the parameters
$\btheta$ are plausible, and the
sampling distribution $p(\bdata | \btheta)$ describes
our initial uncertainty about the data set we're going to observe, as a
function of the unknown parameters $\btheta$.
When the data is known, our state of knowledge about the parameter is
updated from the prior $p(\theta)$ to the posterior distribution given by
Bayes' rule:
\begin{eqnarray}
p(\btheta | \bdata) &=&
\frac{p(\btheta)p(\bdata | \btheta)}
{p(\bdata)}
\end{eqnarray}
where the denominator, often called the {\it evidence} or
{\it marginal likelihood}, is given by:
\begin{eqnarray}
\mathcal{Z} = p(\bdata) = \int p(\btheta) p(\bdata | \btheta) d^N \btheta
\end{eqnarray}

@@

The marginal likelihood was $\ln(\mathcal{Z}) \approx -217.04$.

@@

\section{Reanalysis of Gliese 581}

The red dwarf star Gliese 581 is thought to host several planets. Exactly
how many is a matter of considerable debate. According to \citet{}, there
are two planets whose existence is not doubted, two more whose existence is
doubted by some, and another two thought not to exist by most groups.

Our model cannot distinguish between oscillations due to planets and
oscillations due to stellar activity: any oscillations found in the dataset
will be described as ``planets'' by the model.

@@

The marginal likelihood was $\ln(\mathcal{Z}) \approx -618.04$.
